\documentclass{article}
\usepackage{helvetica}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{tabularx}

%adjust margins
\usepackage{fullpage}
\addtolength{\textwidth}{.75in}
\addtolength{\hoffset}{-.35in}
\addtolength{\textheight}{1.5in}
\addtolength{\voffset}{-.35in}

% disable most hyphenation at the right margin
\hyphenpenalty=10000
\raggedright

\begin{document}
%No page numbers
\pagestyle{empty}

\begin{center}%Title Bar
{\LARGE\bf{Daniel M. Rubin}}\\
76 Orchard St. \#2  $\bullet$  Cambridge, MA 02140  $\bullet$  (707)-478-1241  $\bullet$  \href{mailto:dmrubin3@gmail.com}{dmrubin3@gmail.com} $\bullet$ \href{https://github.com/DrMcTaco}{github.com/DrMcTaco}

%Bring line up to bottom of address/info line
\vspace*{-.5\baselineskip}
\rule{\textwidth}{1pt}

%need space ofter line across page
\addvspace{.2cm}

\begin{tabularx}{\linewidth}{>{\raggedright\bf\large{}}p{3.0cm}X}

%%%%%%%%%%%%%Education%%%%%%%%%%%%%
Education & {\large Northeastern University}, Boston, MA\\
& PhD Physics 2012 - 2018\\
\rule{0pt}{0.5cm} & {\large University of California}, Davis, CA\\
& BSc Physics, 2008 - 2012\\
& \\ %Section Separator do not use if using itemize
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%Skills%%%%%%%%%%%%%
Languages and Tools & Python, SQL, Terraform, Shell Scripting, Avro, JsonSchema, Snowflake, Looker, dbt, MySQL, postgres, Mongodb, Unix administration, docker, AWS Products Including (S3, RDS, Kinesis, EC2, ECS)\\
% LabView/LabWindows, MATLAB, \LaTeX, Arduino\\
 & \\ %Section Separator
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%Experience%%%%%%%%%%%%%
Experience & {\large \textbf{CarGurus}, Principal Data Engineer}, 2021 - Present

{\large Senior Data Engineer}, 2019 - 2021 
\begin{compactitem}
	\item Re-architected a coupled extract and load pipeline into separate scalable components, reducing code complexity and decreasing effort to develop new integrations.
	\item Migrated self-service reporting and analytics tools to a modern platform centered on data-build-tool (dbt), to ease barrier to entry for less technical users.
	\item Took ownership of a client side tracking platform(Snowplow Analytics), processing 100M+ events per day. Owned all aspects and infrastructure post event creation to ingestion into data warehouse.
	\item Developed guidelines and best practices for direct product integrations with the data warehouse.
	\item Served as a member of the CarGurus Server Side Council, a cross-functional group overseeing and providing guidance on the adoption of new tools and technology for the entire Engineering organization.
\end{compactitem}
{\large Data Engineer}, 2018 - 2019
\begin{compactitem}
	\item Developed integrations for a scalable ELT pipeline from both internal and external sources into a Snowflake data warehouse.
	\item Maintained and expanded observability for cloud based distributed architecture for a large scale ELT pipeline, processing 100s of GB per day.
	\item Established a center of excellence for efficient and maintainable analytical SQL.
	\item Translated legacy cloud infrastructure to into infrastructure-as-code (terraform) for ease of maintainability.
\end{compactitem} \\
 & {\large \textbf{NEU Laboratory for Graphene Research}, Graduate Research Assistant}, 2013 - 2018
\begin{compactitem}
	\item Designed, constructed, calibrated, and deployed optoelectronic characterization instrument  used in material characterization with LabView and Python. 
	\item Utilized quantitative computational models for optical spectroscopies of nanomaterials to validate and analyze experimental data.
	\item Modeled electronic structure and properties of semiconductor materials with DFT based simulation packages.
	\item Simulated nuclear processes in various materials using MCNP to model ionizing radiation in the design of radiation detection systems.
 	\item Managed and maintained a Raman spectrometry user facility with users in the Physics, Chemistry, Mechanical Engineering, and Chemical Engineering departments.
 \end{compactitem} \\ 

% Personal Projects & 
% \begin{compactitem}
% 	\item Home-brew soil moisture monitoring station storing data from an external probe in a SQL database. A locally available website can request time series data and dynamically display previous soils moisture readings. All services running on a RaspberryPi.
% 	\item Magic: The Gathering thesaurus. User querriable database of the 15,000+ unique cards with similarity computed using natural language processing techniques. 
% \end{compactitem} \\
%  \rule{0pt}{0.5cm} & {\large Teaching Assistant, Northeastern University Physics Department}, 2012 - 2015\\
%  & Provided in class instruction on introductory physics topics and guided students in developing safe and accurate laboratory procedures in both introductory and advanced lab courses. \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%Patents%%%%%%%%%%%%%
Patents &  \large{Tunable and Reconfigurable Atomically Thin Heterostructures}\\
 & Anthony Vargas, Fangze Liu, Christopher Lane, \textbf{Daniel Rubin}, Ismail Bilgin, Matthew DeCapua, Arun Bansil, Swastik Kar. {\it U.S. Patent Application No. 62/378,345}  (August 2016)\\
\rule{0pt}{0.5cm}  & \large{Ion and Radiation detection Devices Based on Carbon Nanomaterials and Two-Dimensional Materials}\\
 & Ji Hao, Swastik Kar, Yung Joon Jung. \textbf{Daniel Rubin} {\it Intl. Patent Application No. US 2017/051032} (September 2017)\\
 & \\ %Section Separator
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%Publications%%%%%%%%%%%%%
% Publications & \large{ Tunable and Laser-Reconfigurable 2D Heterocrystals Obtained by Epitaxial Stacking of Crystallographically Incommensurate Bi$_{2}$Se$_{3}$ and MoS$_{2}$}\\
%  & Anthony Vargas, Fangze Liu,  Christopher Lane, {\bf Daniel Rubin}, Ismail Bilgin, Matthew DeCapua, Arun Bansil, Swastik Kar. {\it  Science Advances, 14 JUL 2017 : E1601741}\\
%  \rule{0pt}{0.5cm}   & \large{Excitonic processes in atomically-thin MoSe$_2$/MoS$_2$ vertical heterostructures}\\
%  & Victor Carozo, Kazunori Fujisawa, Rahul Rao, Ethan Kahn, Jose Cunha, Tianyi Zhang, {\bf Daniel Rubin}, Andres de Luna Bugallo, Swastik Kar, Mauricio Terrones. 2D Materials {\it Awaiting Publication}\\
%  \rule{0pt}{0.5cm}   & \large{Widely-Tunable Neutral and Charged Excitons at the 2D Interface Between Metal Contacts and Monolayer Molybdenum Disulfide}\\
%  & {\bf Daniel Rubin}, Ismail Bilgin, Swastik Kar. {\it Manuscript submitted, awaiting review.}\\
% \rule{0pt}{0.5cm}  & \large{Characterization of Chalcogen Doping in Atomically thin MoS$_{2}$-MoSe$_{2}$ Hetero-Junctions}\\
%  & Ismail Bilgin and {\bf Daniel Rubin}, Kazunori Fujisawa, Colin Casey, Aditya D. Mohite, Mauricio Terrones, Andres de Luna Bugall, Swastik Kar. \it{Manuscript in Preparation}\\
%  & \\ %Section Separator
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
%%%%%%%%%Presentations%%%%%%%%%
% Presentations & {\large Materials Research Society Fall Meeting 2017}\\
%  & Contributed Talk: Control of Room Temperature Exciton Dynamics in the Contact Region of MoS$_2$ Field Effect Devices.\\
%  & {\large Materials Research Society Fall Meeting 2014}\\
%  & Contributed Talk: Synthesis and Characterization of Few-Layered Black-Phosphorus \\
%  & \\ %Section Separator
%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%Awards and Honors%%%%%%%%%%%%%
%Awards Go here if I had any
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{tabularx}
\end{center}
\end{document}